---
title: "CS 513 Final - Q2"
author: "Aidan Fischer - 10447681"
date: "`r Sys.Date()`"
output: pdf_document
---
Load required libraries and data
```{r}
rm(list=ls())
library(caTools)
library(class)
library(e1071)
library(caret)
library(BBmisc)
data = read.csv("NYNJ_zipcode_population.csv")
data = data[complete.cases(data), ]
```
Take the clustering attributes and normalize
```{r}
datamat = data[,-c(1,2,3)]
rownames(datamat) <- data[,3]
datamat = normalize(datamat, method="scale")
```
Perform hierarchical clustering
```{r}

distmat = stats::dist(datamat, method="euclidean")
state_hclust = hclust(distmat, method="single")
plot(state_hclust)
rect.hclust(state_hclust, k=3, border=2:6)
clusters = cutree(state_hclust,k=3)
```
View cluster assignments for cluster 1
```{r}
print(clusters[clusters==1])
```
View cluster assignments for cluster 2
```{r}
print(clusters[clusters==2])
```
View cluster assignments for cluster 3
```{r}
print(clusters[clusters==3])
```
The algorithm seems to assign most of the zip codes to cluster 1 for some reason when using the single method. I was unable to affect this behavior. I am unsure why. 