---
title: "CS 513 Final - Q3"
author: "Aidan Fischer - 10447681"
date: "`r Sys.Date()`"
output: pdf_document
---
Load required libraries and data
```{r}
rm(list=ls())
library(caTools)
library(class)
library(e1071)
library(caret)
library(BBmisc)
data = read.csv("NYNJ_zipcode_population.csv")
data = data[complete.cases(data), ]
```
Take the clustering attributes and normalize
```{r}
datamat = data[,-c(1,2,3)]
rownames(datamat) <- data[,3]
datamat = normalize(datamat, method="scale")
```
Perform kmeans clustering
```{r}
state_kmeans = kmeans(datamat,5)
```
View cluster assignments for cluster 1
```{r}
print(state_kmeans$cluster[state_kmeans$cluster==1])
```
View cluster assignments for cluster 2
```{r}
print(state_kmeans$cluster[state_kmeans$cluster==2])
```
View cluster assignments for cluster 3
```{r}
print(state_kmeans$cluster[state_kmeans$cluster==3])
```
View cluster assignments for cluster 4
```{r}
print(state_kmeans$cluster[state_kmeans$cluster==4])
```
View cluster assignments for cluster 5
```{r}
print(state_kmeans$cluster[state_kmeans$cluster==5])
```
KMeans did a much better job at clustering more evenly than single linkage hierarchal clustering did. 